### 2009-09-10 doc/tech_doc/chelonia/arc-storage-documentation.tex
renaming arc_storage_cli to chelonia

In the prototype release there is a command-line client tool called \verb!arc_storage_cli!, which is written in Python, and only need a basic Python installation to run. It is capable of communicating with a given Bartender service, and can upload and download files via HTTP. However, in order to use proxy certificates or to transfer files with the GridFTP protocol, the ARC client libraries must also be installed.

@@

The \verb!arc_storage_cli! has its built-in help. The methods can be listed by giving the command without arguments:

\begin{verbatim}
$ arc_storage_cli
Usage:
  arc_storage_cli <method> [<arguments>]
  Supported methods: stat, make[Collection], unmake[Collection], list, move,
    put[File], get[File], del[File], pol[icy], unlink,
    credentialsDelegation, removeCredenstials
\end{verbatim}
Without arguments, each method prints its own help, e.g., for the move method:
\begin{verbatim}
$ arc_storage_cli move
Usage: move <sourceLN> <targetLN>
\end{verbatim}

@@

\begin{verbatim}
$ cat testfile 
This is a testfile.
$ arc_storage_cli put testfile /tmp/
- The size of the file is 20 bytes
- The md5 checksum of the file is 9a9dffa22d227afe0f1959f936993a80
- Calling the Bartender's putFile method...
- done in 0.08 seconds.
- Got transfer URL: http://localhost:60000/hopi/d15900f5-34ee-4bba-bb10-73d60d1c0d75
- Uploading from 'testfile'
    to 'http://localhost:60000/hopi/d15900f5-34ee-4bba-bb10-73d60d1c0d75' with http...
Uploading 20 bytes... data sent, waiting... done.
- done in 0.0042 seconds.
'testfile' (20 bytes) uploaded as '/tmp/testfile'.
$ arc_storage_cli stat /tmp/testfile
- Calling the Bartender's stat method...
- done in 0.05 seconds.
'/tmp/testfile': found
  states
    checksumType: md5
    neededReplicas: 1
    size: 20
    checksum: 9a9dffa22d227afe0f1959f936993a80
  timestamps
    created: 1210232135.57
  parents
    51e12fab-fd3d-43ec-9bc5-17041da3f0b2/testfile: parent
  locations
    http://localhost:60000/Shepherd fc0d3d99-6406-4c43-b2eb-c7ec6d6ab7fe: alive
  entry
    type: file
$ arc_storage_cli get /tmp/testfile newfile
- Calling the Bartender's getFile method...
- done in 0.05 seconds.
- Got transfer URL: http://localhost:60000/hopi/dab911d0-110f-468e-b0c3-627af6e3af31
- Downloading from 'http://localhost:60000/hopi/dab911d0-110f-468e-b0c3-627af6e3af31'
    to 'newfile' with http...
Downloading 20 bytes... done.
- done in 0.0035 seconds.
'/tmp/testfile' (20 bytes) downloaded as 'newfile'.
$ cat newfile 
This is a testfile.
\end{verbatim}

@@

\textbf{ARCFS}, a Filesystem in Userspace (FUSE) module, provides high-level access to the storage system. FUSE provides a simple library and a kernel-userspace interface. Using FUSE and the ARC Python interface, ARCFS allows users to mount the storage namespace into the local namespace, enabling the use of operating system commands and tools such as graphical file browsers. Delegation handling is not yet implemented in the fuse module, so that to change ownership, group access, etc., the \verb!arc_storage_cli! tool must be used.

As for the \verb!arc_storage_cli! the credentials of the user and the URL of the Bartender can be configured either with an XML file located at \verb!~/.arc/client.xml! or with environment variables. See Section \ref{sub:prototype_cli_tool} for more details.

@@

\begin{verbatim}
$ python arcfs.py ./mnt
$ cat testfile
This is a test file
$ mkdir mnt/tmp
$ cp testfile mnt/tmp
$ ls -l mnt/tmp/testfile
-rw-r--r-- 1 jonkni jonkni 20 2009-03-21 23:27 mnt/tmp/testfile
$ cp mnt/tmp/testfile newfile
$ cat newfile
This is a test file
$ cat mnt/tmp/testfile
This is a test file
$ fusermount -u ./mnt
$ arc_storage_cli stat /tmp/testfile
- Calling the Bartender's stat method...
- done in 0.05 seconds.
'/tmp/testfile': found
  states
    checksumType: md5
    neededReplicas: 1
    size: 20
    checksum: 9a9dffa22d227afe0f1959f936993a80
  timestamps
    created: 1210232135.57
  parents
    51e12fab-fd3d-43ec-9bc5-17041da3f0b2/testfile: parent
  locations
    http://localhost:60000/Shepherd fc0d3d99-6406-4c43-b2eb-c7ec6d6ab7fe: alive
  entry
    type: file
\end{verbatim}

@@

As with the \verb!arc_storage_cli! command the credentials of the user and the URL of the Bartender can be configured with an XML file located at \verb!~/.arc/client.xml!. When the ARC DMC is initiated, it will create an instance of \verb!DataPointARC! which provides functionality for listing collections and file IO. When downloading/uploading files from/to the storage system, the data point will use the provided Bartender URL to acquire a TURL from a Bartender. This TURL will be given to a \verb!DataTransfer! handle. Calling the constructor of the DataHandle class with a URL will trigger the iGetDataPoint class of all registered DMC's to be called until a non-NULL pointer is returned. This means that as long as there exists a data point plugin for the protocol of the returned TURL, the transfer will proceed.

>>>>

In the prototype release there is a command-line client tool called \verb!chelonia!, which is written in Python, and only need a basic Python installation to run. It is capable of communicating with a given Bartender service, and can upload and download files via HTTP. However, in order to use proxy certificates or to transfer files with the GridFTP protocol, the ARC client libraries must also be installed.

@@

The \verb!chelonia! has its built-in help. The methods can be listed by giving the command without arguments:

\begin{verbatim}
$ chelonia
Usage:
  chelonia <method> [<arguments>]
  Supported methods: stat, make[Collection], unmake[Collection], list, move,
    put[File], get[File], del[File], pol[icy], unlink,
    credentialsDelegation, removeCredenstials
\end{verbatim}
Without arguments, each method prints its own help, e.g., for the move method:
\begin{verbatim}
$ chelonia move
Usage: move <sourceLN> <targetLN>
\end{verbatim}

@@

\begin{verbatim}
$ cat testfile 
This is a testfile.
$ chelonia put testfile /tmp/
- The size of the file is 20 bytes
- The md5 checksum of the file is 9a9dffa22d227afe0f1959f936993a80
- Calling the Bartender's putFile method...
- done in 0.08 seconds.
- Got transfer URL: http://localhost:60000/hopi/d15900f5-34ee-4bba-bb10-73d60d1c0d75
- Uploading from 'testfile'
    to 'http://localhost:60000/hopi/d15900f5-34ee-4bba-bb10-73d60d1c0d75' with http...
Uploading 20 bytes... data sent, waiting... done.
- done in 0.0042 seconds.
'testfile' (20 bytes) uploaded as '/tmp/testfile'.
$ chelonia stat /tmp/testfile
- Calling the Bartender's stat method...
- done in 0.05 seconds.
'/tmp/testfile': found
  states
    checksumType: md5
    neededReplicas: 1
    size: 20
    checksum: 9a9dffa22d227afe0f1959f936993a80
  timestamps
    created: 1210232135.57
  parents
    51e12fab-fd3d-43ec-9bc5-17041da3f0b2/testfile: parent
  locations
    http://localhost:60000/Shepherd fc0d3d99-6406-4c43-b2eb-c7ec6d6ab7fe: alive
  entry
    type: file
$ chelonia get /tmp/testfile newfile
- Calling the Bartender's getFile method...
- done in 0.05 seconds.
- Got transfer URL: http://localhost:60000/hopi/dab911d0-110f-468e-b0c3-627af6e3af31
- Downloading from 'http://localhost:60000/hopi/dab911d0-110f-468e-b0c3-627af6e3af31'
    to 'newfile' with http...
Downloading 20 bytes... done.
- done in 0.0035 seconds.
'/tmp/testfile' (20 bytes) downloaded as 'newfile'.
$ cat newfile 
This is a testfile.
\end{verbatim}

@@

\textbf{ARCFS}, a Filesystem in Userspace (FUSE) module, provides high-level access to the storage system. FUSE provides a simple library and a kernel-userspace interface. Using FUSE and the ARC Python interface, ARCFS allows users to mount the storage namespace into the local namespace, enabling the use of operating system commands and tools such as graphical file browsers. Delegation handling is not yet implemented in the fuse module, so that to change ownership, group access, etc., the \verb!chelonia! tool must be used.

As for the \verb!chelonia! the credentials of the user and the URL of the Bartender can be configured either with an XML file located at \verb!~/.arc/client.xml! or with environment variables. See Section \ref{sub:prototype_cli_tool} for more details.

@@

\begin{verbatim}
$ python arcfs.py ./mnt
$ cat testfile
This is a test file
$ mkdir mnt/tmp
$ cp testfile mnt/tmp
$ ls -l mnt/tmp/testfile
-rw-r--r-- 1 jonkni jonkni 20 2009-03-21 23:27 mnt/tmp/testfile
$ cp mnt/tmp/testfile newfile
$ cat newfile
This is a test file
$ cat mnt/tmp/testfile
This is a test file
$ fusermount -u ./mnt
$ chelonia stat /tmp/testfile
- Calling the Bartender's stat method...
- done in 0.05 seconds.
'/tmp/testfile': found
  states
    checksumType: md5
    neededReplicas: 1
    size: 20
    checksum: 9a9dffa22d227afe0f1959f936993a80
  timestamps
    created: 1210232135.57
  parents
    51e12fab-fd3d-43ec-9bc5-17041da3f0b2/testfile: parent
  locations
    http://localhost:60000/Shepherd fc0d3d99-6406-4c43-b2eb-c7ec6d6ab7fe: alive
  entry
    type: file
\end{verbatim}

@@

As with the \verb!chelonia! command the credentials of the user and the URL of the Bartender can be configured with an XML file located at \verb!~/.arc/client.xml!. When the ARC DMC is initiated, it will create an instance of \verb!DataPointARC! which provides functionality for listing collections and file IO. When downloading/uploading files from/to the storage system, the data point will use the provided Bartender URL to acquire a TURL from a Bartender. This TURL will be given to a \verb!DataTransfer! handle. Calling the constructor of the DataHandle class with a URL will trigger the iGetDataPoint class of all registered DMC's to be called until a non-NULL pointer is returned. This means that as long as there exists a data point plugin for the protocol of the returned TURL, the transfer will proceed.
